An anthropological account of the Vim editor:\\ ouroboros, features and tweaks after 10 years of usage

### 2017-11-12 article/article.tex
ideas for enhancements

\subsubsection{Ex}
One might use the normal commands \tttt{q(:,/,?)} to have a window
with colon or search command history to be edited normaly,
and the chosen command can be run with \ttt{CR}.
Vimscript was largerly based on the ex editor~\cite{ex},
and a more advanced user might use it for prototyping
by defining mappings and settings and managing sessions and scripts
propably in a \tttt{plugin/} folder of a directory in \tttt{:echo \&runtimepath}.
In the default interface started with the \tttt{Q} command in normal mode,
each command is input without entering : again. Use \tttt{:vi} to exit Ex mode,
follow documentation from \tttt{:h Ex-mode} for further information.

@@

>>>>

\subsubsection{Ex}
One might use the normal commands \tttt{q(:,/,?)} to have a window
with colon or search command history to be edited normaly,
and the chosen command can be run with \ttt{CR}.
Vimscript was largerly based on the ex editor~\cite{ex},
and a more advanced user might use it for prototyping
by defining mappings and settings and managing sessions and scripts
propably in a \tttt{plugin/} folder of a directory in \tttt{:echo \&runtimepath}.
In the default interface started with the \tttt{Q} command in normal mode,
each command is input without entering : again. Use \tttt{:vi} to exit Ex mode,
follow documentation from \tttt{:h Ex-mode} for further information.
I might be loosing something, but for most
hacking I use the command-line window accessed with \tttt{q:}.
I find it comfortable to browse the history in a normal-like mode,
and edit them also using the insert mode as usual.
The mapping have to be defined as autocommands as in~\cite{vimrc}.

@@

      \item Colorschemes for true color (gui).
        The standard colors (e.g. blue, elflord) loose some of the distinctions,
        e.g. SpellBad tokens are not highlighted on these colorschemes
        it you have a functioning \tttt{se termguicolors} (standard GUI mode
        and available in terminals since recent versions of Vim 8, see Section~\ref{visual2}). In~\cite{vimrc} are some lines that make such colorschemes after over
        \tttt{:colorscheme blue}.
        This design of color schemes over the standard color schemes might be
        a very simple and effective way to make new color schemes.
